Working with Code environments in texor

### 2023-07-22 supplement/code-env/code-example.tex
Updated code env supplementary material

Hence Texor package uses the stream editor to search find and replace matching code environments to verbatim before pandoc touches it.

This way the the code is not lost in conversion, also a pandoc extension is used to add attributes to the markdown code using 
'fenced\_code\_attributes'

@@

\begin{table}[htbp]
\centering
\begin{tabular}{l | lllll }
 \hline
 Code Environment Type &  &  &  & & \\
 \hline
 Example          & example & example* & smallexample & & \\
 S.series         & Sin & Sout & Sinput & Soutput & Scode \\
 Special Verbatim & smallverbatim & boxedverbatim &  & & \\
\hline
\end{tabular}
\caption{Code Environment support in texor}
\label{table:1}
\end{table}

@@

2. smallverbatim :

\begin{smallverbatim}
print("Hello world")
\end{smallverbatim}

3. boxedverbatim :

@@

3. smallexample :

\begin{smallexample}
print("Hello world")
\end{smallexample}

\section{Code in Figure Environments}
A small example of this is visble in \ref{code:example}

@@

\section{Code in Table Environments}
We can use code environments in a table using minipage environments.

Table \ref{table:2} is an example of table with code environments within a table.

@@

\section{Inline Code usage}

@@

In summary the \CRANpkg{texor} package supports:
\begin{itemize}
\item Almost all code environments in RJournal.
\item Code Highlight for R language.
\item Code blocks inside Figure environment with captions.
\item Inline Code.
\end{itemize}

>>>>

Hence \CRANpkg{texor} package uses the stream editor to search find and replace matching code environments to verbatim before pandoc touches it.

This way the the code is not lost in conversion, also a pandoc extension is used to add attributes to the markdown code using  \verb|fenced_code_attributes|

@@

\begin{table}[htbp]
\centering
\begin{tabular}{l | lllll }
 \hline
 Code Environment Type &  &  &  & & \\
 \hline
 Example          & example & example* &  & & \\
 S.series         & Sin & Sout & Sinput & Soutput & Scode \\
 Special Verbatim & boxedverbatim & &  & & \\
\hline
\end{tabular}
\caption{Code Environment support in texor}
\label{table:1}
\end{table}

@@

2. boxedverbatim :

@@

% Code in Figures
\section{Code in Figure Environments}
A small example of this is visble in \ref{code:example}

@@

% Code in Tables
\section{Code in Table Environments}
We can use code environments in a table using minipage environments.

Table \ref{table:2} is an example of code environments within a table.

@@

% Inline Code
\section{Inline Code usage}

@@

In summary the \CRANpkg{texor} package supports:
\begin{itemize}
\item Almost all code environments in RJournal.
\item Code Highlight for R language.
\item Inline Code.
\item Code in different environments like tables/figures.
\end{itemize}
